### 2012-06-19 inst/examples/voi_sethi_parameters.Rmd
voi with sethi parameterization

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information/", verbose=TRUE or`

@@

We consider a Beverton Holt state equation governing population dynamics, \\( f(x,h) = \frac{A x}{1 + B x} \\)

``` {r }
f <- BevHolt
````

With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.05`.

``` {r }
pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
````

Note that the positive stationary root of the model is given by \\( \frac{A-1}{B} \\), or carring capacity `K` = `r K`.  
We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  \\( \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\),

``` {r  profit}
price <- 1
c0 <- 0.01
c1 <- 0
profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
````

with price `r price`, `c0` `r c0` and `c1` `r c1`.

@@

  z_g <- function() rlnorm(1,  0, policy_g) 
  z_m <- function() rlnorm(1,  0, policy_m) 
  z_i <- function() rlnorm(1,  0, policy_i)

@@

``` {r runall}
det <- scenario(0, 0.0, 0.0)
g <- scenario(0.2, 0.0, 0.0)
m <- scenario(0.0, 0.2, 0.0)
i <- scenario(0.0, 0.0, 0.2)
gm <- scenario(0.2, 0.2, 0.0)
gi <- scenario(0.2, 0.0, 0.2)
gmi <- scenario(0.2, 0.2, 0.2)
````

``` {r not_all_zero}
det <- scenario(0.01, 0.0, 0.0)
````

@@

``` {r sethiplots, dependson="runall"}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) + ylab("escapement") 
ggplot(policy) + geom_smooth(aes(stock, stock-x_grid[value], color=variable))+ ylab("escapement")

value <- melt(data.frame(stock = x_grid, det=det$V, g = g$V, m = m$V, gm = gm$V, gi = gi$V, gmi = gmi$V), id = "stock")
ggplot(value) + geom_point(aes(stock, value, color=variable)) + ylab("Net Present Value")
ggplot(value) + geom_smooth(aes(stock, value, color=variable)) + ylab("Net Present Value")
````

@@

``` {r profits_time, fig.cap="The profits made in each time interval of a single replicate, by scenario", dependson="tidyall"}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)

````

@@

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- c("deter", "growth", "measure", "implement", "growth+measure", "growth+implement", "all")
print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
````

@@

``` {r biblio, echo=FALSE, results="asis"}
print(knitcitations::bibliography(), "html")
````

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters/", verbose=TRUE or`

@@

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, cache.path="value_of_information/" or`

Chose the state equation / population dynamics function

``` {r }
f <- function(x,h,p){
	S = x - h
	p[1] * S * (1 - S/p[2]) + S
}
````

With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.

``` {r }
pars <- c(r, K)
````

We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  \\( \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\),

``` {r  profit}
price <- 1
c0 <- 0.0
c1 <- 0
profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
````

with price = `r price`, `c0` = `r c0` and `c1` = `r c1`.

@@

  z_g <- function() 1+(2*runif(1, 0,  1)-1) * policy_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * policy_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * policy_i

@@

``` {r runall}
det <- scenario(0.1, 0.0, 0.0)
g   <- scenario(0.5, 0.0, 0.0)
m   <- scenario(0.0, 0.5, 0.0)
i   <- scenario(0.0, 0.0, 0.5)
gm  <- scenario(0.5, 0.5, 0.0)
gi  <- scenario(0.5, 0.0, 0.5)
im  <- scenario(0.0, 0.5, 0.5)
gmi <- scenario(0.5, 0.5, 0.5)
````

@@

``` {r sethiplots, dependson="runall"}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], i= m$D[,i], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) 
	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) + ylab("escapement")

ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) 
	geom_smooth(aes(stock, x_grid[value], color=variable)) + ylab("harvest")

value <- melt(data.frame(stock = x_grid, det=det$V, g = g$V, m = m$V, gm = gm$V, gi = gi$V, gmi = gmi$V), id = "stock")
ggplot(value) + geom_point(aes(stock, value, color=variable)) +
	ggplot(value) + geom_smooth(aes(stock, value, color=variable)) + ylab("Net Present Value")
````

@@

@@

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- c("deterministic", "growth", "measure", "implement", "growth+measure", "growth+implement", "measure+implement", "all")
print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
````

@@

``` {r biblio, echo=FALSE, results="asis"}
print(knitcitations::bibliography(), "html")
`
